Regression

### 2015-08-28 Regression.rmd
done with random forest

#RMSE = 0.49246
#compared to non-cross validated
# RMSE = 0.4759
```

>>>>

#RMSE = 0.49246
#compared to non-cross validated
# RMSE = 0.4759

#try using caret package on code.client
fit<- train(return.pdol ~ inv.mlsto.log + Discipline + timespan.cbrt + no.users + pc.pro + Business + 
                      inv.mlsto.log*pc.pro + inv.mlsto.log*Business + code.client,
              data=all7d,
            method = 'lm', trControl = tc)

### 2015-08-28 rand_forest.rmd
done with random forest

@@

@@

        add.mult = randomForest(as.formula(formula),mtry=5, ntree=500, data = reduced)

        #perform 10 fold xval using caret package
        tc = trainControl("cv",5)
        #keep cp static at 0.011
        rf.grid = expand.grid(mtry= 5:6)
        train.rf = train(as.formula(formula), data=df, method="rf",trControl=tc,
                  tuneGrid=rf.grid)

@@

>>>>

addmult(var= c('pc.majpos', 'majority.pos','JD.Second'), min.Year = 2008, df= all7d)

test<- all7d[complete.cases(all7d[,c('code.client','pc.majpos')]) &
                     all7d$Year>2008 & all7d$Discipline == 'Structural',]
test$code.client<- droplevels(test$code.client)
test %>% str

@@

addmult<- function(var= c('pc.majpos','majority.pos', 'code.client', 'code.contact'), min.Year = 2008, df= all7d, 
                   Disc= "Structural"){
        #subset data frame based on complete cases with additional variables
        reduced = df[complete.cases(df[,var]) & df$Year>min.Year & df$Discipline == Disc,]

        if('code.client' %in% var){
        sample = factor(sample(unique(reduced$code.client),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.client %in% sample,]

        reduced$code.client= factor(reduced$code.client)
        }

        if('code.contact' %in% var){
        sample1 = factor(sample(unique(reduced$code.contact),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.contact %in% sample1,]

        reduced$code.contact= factor(reduced$code.contact)
        }

        #make formula
        formula = paste("return.pdol ~ inv.mlsto + timespan + no.users + pc.pro + 
                     client.totinv + code.director + 
                  Num.disc + Business + Biz.type")

@@

        #make forest
        red.forest= randomForest(as.formula(formula), data=reduced, mtry=5,ntree=500,importance=TRUE)

        print(
                varImpPlot(red.forest)
        )

        #perform 10 fold xval using caret package
        tc = trainControl("cv",5)
        #keep cp static at 0.011
        rf.grid = expand.grid(mtry= 5)
        train.rf = train(as.formula(formula), data=df, method="rf",trControl=tc,
                  tuneGrid=rf.grid)

@@

addmult(var= c('pc.majpos','majority.pos', 'code.client'), min.Year = 2008, df= all7d, 
                   Disc= "Structural")

#with code.client i'm still getting 48.9 cents RMSE! that sucks!!!! with linear regression i was getting

addmult(var= c('pc.majpos','majority.pos','code.contact'), min.Year = 2008, df= all7d, 
                   Disc= "Structural")
#50.6 cents
#importance levels of code.client and code.contact are up there but they're not THAT high. like midway out of all options.
